\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-23 manuscript.Rnw
Add references for data.table and rcpp

\pkg{hesim} is an \proglang{R} package that advances the functionality and performance of the existing software. Multiple model types are supported including cohort discrete time state transition models (cDTSTMs), N-state PSMs, and individual-level continuous time state transition models (iCTSTMs), encompassing both Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. To maximize flexibility and facilitate integration of the statistical methods and economic model, parameters can be set by either fitting models in \proglang{R} or by inputting values obtained from external sources. So that individual-level simulation and PSA can be run quickly, \pkg{Rcpp} and \pkg{data.table} are heavily utilized. After simulating costs and quality-adjusted life-years (QALYs) from a PSA, decision analysis can be performed within a cost-effectiveness framework.

>>>>

\pkg{hesim} is an \proglang{R} package that advances the functionality and performance of the existing software. Multiple model types are supported including cohort discrete time state transition models (cDTSTMs), N-state PSMs, and individual-level continuous time state transition models (iCTSTMs), encompassing both Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. To maximize flexibility and facilitate integration of the statistical methods and economic model, parameters can be set by either fitting models in \proglang{R} or by inputting values obtained from external sources. So that individual-level simulation and PSA can be run quickly, \pkg{Rcpp} \citep{eddelbuettel2011rcpp, eddelbuettel2013rcpp, eddelbuettel2018rcpp} and \pkg{data.table} \citep{dowle2021datatable} are heavily utilized. After simulating costs and quality-adjusted life-years (QALYs) from a PSA, decision analysis can be performed within a cost-effectiveness framework.
